---
title: "WUP_04"
author: "Abel Jacobo Perez"
date: "09-16-2021"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(knitr)
require(tidyverse)
require(tigerstats)
WordData=read.csv("GSScsv.csv")
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

The data is in the file GSScsv.csv and came from the 2018 General Social Survey.  The question to answer is to resolve this hypothesis.  
$H_0$ There is no difference between the average score on the WORDSUM test and level of schooling DEGREE  
$H_a$ There is a significant difference in average score on the WORDSUM test between at least two levels of DEGREE  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
basicCN <- ggplot(WordData,aes(x=DEGREE,y=WORDSUM))

basicCN + geom_boxplot()
```
This boxplot shows us that the longer the students were in school ,the higher thier average wordsum. This boxplot shows that the median Graduate scored the highest level of wordsum at 11.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
favstats(WORDSUM~DEGREE,data=WordData)
```
the median of the Graduates is the higest median wordsum at 11, and the highest mean as well at 10.095.

The lowest mean wordsum levels were from the LT highschool (8) whom also scored the lowest mean wordsum at 7.75

we can see that the longer you stay in school the higher your wordsum.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
model1 <- aov(WORDSUM~DEGREE,data=WordData)
summary.aov(model1)
```
The p value is too low at 0.000236,so I reject the Null hypothesis , the number is so low that the probability of getting the result that we found is extremely low.

```{r}
#we specify the margins starting at the bottom and proceeding clockwise - thus 8.7 is the left side margin to hold the names of the factors
par(mar = c(3, 16, 2, 2))
plot(TukeyHSD(model1),las=2)
```


The tukey shows that the LT highschool graduate and highschool graduate have the lowest wordsum and they don't even touch 0 like the rest of graduate levels .Thus there is a significant difference between the word sum for those who continued in school longer and those who only finished Lt higschool graduate and highscool graduate . 

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

We reject the Null hypothesis because the P value is too low; P value:0.000236 We found that there are are signicant difference between the wordsum of the LT high school and High school graduates.The college student all had a higher wordsum then those who only finished highschool.
